Identifying covariate traits of trance and possession phenomena in the Ethnographic

### 2022-10-30 Readme.Rmd
new figure

library(tidyverse)
library(glue)
library(knitr)
library(patchwork)
library(corrplot)

@@

@@

ld %>% 
  filter(var_title == 'Trance states', !is.na(code)) %>% 
  count(code, var_description, name = 'n in EA') %>% 
  left_join(trance) %>% 
  arrange(code) %>% 
  rename(Coding = code, Description = var_description) %>% 
  select(Coding,Description,possession_trance,`n in EA`,`n in SCCS`) %>% 
  kable('simple')
```

@@

```{r }
pred_table = read_tsv('data/pred_table_added.tsv')
pred_table %>% 
  kable('simple')
```

@@

cm1a %>% 
  mutate(original = c(names(cm1a)[!names(cm1a) %in% c('Error','Rate')],'Total')) %>% 
  relocate(original) %>% 
  kable('simple', digits = 2)

@@

@@

@@

bayes factor
```{r }
kable(bf, 'simple', digits = 2)
```

>>>>

library(tidyverse)
library(glue)
library(knitr)
library(patchwork)
library(corrplot)
library(ggthemes)
library(ggfortify)
library(ggmap)
library(googlesheets4)

mapWorld = map_data('world', wrap=c(-25,335), ylim=c(-55,75)) # pacific centered

@@

Here is a map of trance and possession phenomena.

```{r fig.width=18, fig.height=5}
lld = ld %>% 
  filter(var_id == 'EA112') %>% 
  mutate(
    lon2 = ifelse(lon < -20, lon + 360, lon),
    var_short = case_when(
      code == 1 ~ 'T',
      code == 2 ~ 'P',
      code == 3 ~ 'T,P,T iff P',
      code == 4 ~ 'T,P,T if P',
      code == 5 ~ 'T,P,T and P',
      code == 6 ~ 'P,T if P',
      code == 7 ~ 'T,P if T',
      code == 8 ~ 'none'
    ),
    coding = fct_reorder(var_name,code)
  )

p1 = ggplot() + 
  geom_polygon(data = mapWorld, aes(x=long, y = lat, group = group)) + 
  geom_label(data = lld, aes(x = lon2, y = lat, colour = coding, label = code)) +
  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks=element_blank(), axis.title.y=element_blank(), axis.text.y=element_blank()) +
  scale_colour_viridis_d() +
  theme_void()

p1 + plot_layout(guides = 'collect')
```

@@

table1 = ld %>% 
  filter(var_title == 'Trance states', !is.na(code)) %>% 
  count(code, var_description, name = 'n in EA') %>% 
  left_join(trance) %>% 
  arrange(code) %>% 
  rename(Coding = code, Description = var_description) %>% 
  select(Coding,Description,possession_trance,`n in EA`,`n in SCCS`)

#write_sheet(table1, ss = 'https://docs.google.com/spreadsheets/d/1X7ZCnw6LVhjLIy4SiSeK3iZ6o1S144iHMv4DqOaCDEU/edit#gid=0', sheet = 'Table 1')

table1 %>% 
  kable('simple')
```

@@

```{r }
pred_table = read_tsv('data/pred_table_added.tsv')

#write_sheet(pred_table, ss = 'https://docs.google.com/spreadsheets/d/1X7ZCnw6LVhjLIy4SiSeK3iZ6o1S144iHMv4DqOaCDEU/edit#gid=0', sheet = 'Table 3')

pred_table %>% 
  kable('simple')
```

@@

table4 = cm1a %>% 
  mutate(original = c(names(cm1a)[!names(cm1a) %in% c('Error','Rate')],'Total')) %>% 
  relocate(original)

#write_sheet(table4, ss = 'https://docs.google.com/spreadsheets/d/1X7ZCnw6LVhjLIy4SiSeK3iZ6o1S144iHMv4DqOaCDEU/edit#gid=0', sheet = 'Table 4')

table4 %>% 
  kable('simple', digits = 2)

@@

#write_sheet(cm1b, ss = 'https://docs.google.com/spreadsheets/d/1X7ZCnw6LVhjLIy4SiSeK3iZ6o1S144iHMv4DqOaCDEU/edit#gid=0', sheet = 'Table 5')

@@

#write_sheet(vars2, ss = 'https://docs.google.com/spreadsheets/d/1X7ZCnw6LVhjLIy4SiSeK3iZ6o1S144iHMv4DqOaCDEU/edit#gid=0', sheet = 'Table 6')

@@

bayes factor
```{r }
#write_sheet(bf, ss = 'https://docs.google.com/spreadsheets/d/1X7ZCnw6LVhjLIy4SiSeK3iZ6o1S144iHMv4DqOaCDEU/edit#gid=0', sheet = 'Table 7')
kable(bf, 'simple', digits = 2)
```
